On the dynamic assessment of the Local-Maximum Entropy Material Point Method through an Explicit Predictor-Corrector Scheme

### 2020-09-11 LME-MPM.tex

\textcolor{blue}{The following test is intended to validate the ability of the discussed time integration schemes in order to reproduce the wave propagation in 2D. The impact of an elastic square plate against a vertical wall is assessed. The square plate dimensions are 50 x 50 m and their elastic parameters are:
\begin{itemize} 
\item  Initial density : $20\ kg/m^3$
\item  Poisson ratio : $0.3$
\item  Elastic modulus : $0.1\ MPa$
\end{itemize}
}
\textcolor{blue}{The background set of nodes is composed by a cartesian grid with an uniform spatial discretisation of 1 m. Four material points per cell are considered. The Courant number is fixed to 0.1 during the whole simulation and $\text{LME}_{3.0}$ shape functions are employed. A horizontal velocity of the square plate of $\text{V}_0 = 1.0 m/s$ \textcolor{green}{is considered} until the \sout{shock} \textcolor{green}{the plate impacts} against the obstacle \textcolor{green}{generating stress waves}. \textcolor{green}{The obstacle is} \sout{which has been} modelled as a set of nodes with prescribed velocity equal to zero. \sout{Stress waves are produced by the aforementioned shock what causes the square to bounce back}. Both \acrshort{npc} and \acrshort{fe} schemes are compared. Spatial distribution of the velocity field inside the square plate obtained with both schemes at different times are given in figure ~\ref{fig:Magnitude_velocity_impact_square}}. 
%%%%%%%%%%%%%%%%
\begin{figure}
%\sidecaption
  \centering
  \resizebox{\hsize}{!}{
\includegraphics[scale=1]{Figures/Velocity_FE_vs_NPC_square.png} 
  }
  \caption{Spatial distribution of the magnitude of the velocity field in an elastic square plate impacted on the right edge. The top row depicts the \acrshort{npc} results meanwhile the bottom row represents the \acrshort{fe} ones at different instants.}
  \label{fig:Magnitude_velocity_impact_square}
\end{figure}
%%%%%%%%%%%%%%%% 
\textcolor{blue}{At early times, \acrshort{npc} and \acrshort{fe} behave in a similar manner. However, at later times, the \acrshort{fe} scheme introduces significant numerical noise compared with the \acrshort{npc} one. \sout{At the end of the simulation, the filtering process when \acrshort{npc} is used leads to a negligible loss of mechanical energy (about 0.1\%).}}

>>>>

\textcolor{blue}{This benchmark has been conveniently adapted from the one proposed by  Hammerquist \& Nairn (2017)~\cite{HAMMERQUIST2017724}, it is intended to validate the ability of the discussed time integration schemes in order to reproduce the wave propagation in 2D. The impact of an elastic square plate against a vertical wall is assessed. The square plate dimensions are 50 x 50 m and their elastic parameters are:
\begin{itemize} 
\item  Initial density : $20\ kg/m^3$
\item  Poisson ratio : $0.3$
\item  Elastic modulus : $0.1\ MPa$
\end{itemize}
}
\textcolor{blue}{The background set of nodes is composed by a cartesian grid with an uniform spatial discretisation of 1 m. Four material points per cell are considered. The Courant number is fixed to 0.1 during the whole simulation and $\text{LME}_{3.0}$ shape functions are employed. A horizontal velocity of the square plate of $\text{V}_0 = 1.0 m/s$ \textcolor{green}{is considered} until the \sout{shock} \textcolor{green}{the plate impacts} against the obstacle \textcolor{green}{generating stress waves}. \textcolor{green}{The obstacle is} \sout{which has been} modelled as a set of nodes with prescribed velocity equal to zero. \sout{Stress waves are produced by the aforementioned shock what causes the square to bounce back}. Both \acrshort{npc} and \acrshort{fe} schemes are compared. Spatial distribution of the velocity field inside the square plate obtained with both schemes at different times are given in figure ~\ref{fig:Magnitude_velocity_impact_square}}. 
%%%%%%%%%%%%%%%%
\begin{figure}
%\sidecaption
  \centering
  \resizebox{\hsize}{!}{
\includegraphics[scale=1]{Figures/Velocity_FE_vs_NPC_square.png} 
  }
  \caption{Spatial distribution of the magnitude of the velocity field in an elastic square plate impacted on the right edge. The top row depicts the \acrshort{npc} results meanwhile the bottom row represents the \acrshort{fe} ones at different instants.}
  \label{fig:Magnitude_velocity_impact_square}
\end{figure}
%%%%%%%%%%%%%%%% 
\textcolor{blue}{At early times, \acrshort{npc} and \acrshort{fe} behave in a similar manner. However, at later times, the \acrshort{fe} scheme introduces significant numerical noise compared with the \acrshort{npc} one. \sout{At the end of the simulation, the filtering process when \acrshort{npc} is used leads to a negligible loss of mechanical energy (about 0.1\%).}}
